%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[9pt]{resume} % Default font size, values from 8-12pt are recommended

%----------------------------------------------------------------------------------------

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\begin{minipage}[t]{0.45\textwidth} % 45% of the page width for name
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% If your name is very short, use just one of the lines below
	% If your name is very long, reduce the font size or make the minipage wider and reduce the others proportionately
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Andres}}}}} % First name
	
	\colorbox{black}{{\HUGE\textcolor{white}{\textbf{\MakeUppercase{Barreto}}}}} % Last name
	
	\vspace{6pt}
	
	{\huge Software Engineer} % Career or current job title
\end{minipage}
\begin{minipage}[t]{0.30\textwidth} % 30% of the page width for the first row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{MapMarker}{9}{Ecuador}\\
	% \icon{Phone}{9}{+1 (212) 347-5627}\\
	\icon{At}{9}{\href{mailto:andres@andresbarreto.net}{andres@andresbarreto.net}}\\	
\end{minipage}
\begin{minipage}[t]{0.275\textwidth} % 27.5% of the page width for the second row of icons
	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
	% The first parameter is the FontAwesome icon name, the second is the box size and the third is the text
	% Other icons can be found by referring to fontawesome.pdf (supplied with the template) and using the word after \fa in the command for the icon you want
	\icon{Globe}{9}{\href{https://andresbarreto.net/}{andresbarreto.net}}\\
	\icon{Github}{9}{\href{https://github.com/andresebr}{github.com/andresebr}}\\
	\icon{Linkedin}{9}{\href{https://www.linkedin.com/in/andresebr/}{linkedin.com/in/andresebr}}\\
\end{minipage}

\vspace{0.5cm}

%----------------------------------------------------------------------------------------
%	INTRODUCTION, SKILLS AND TECHNOLOGIES
%----------------------------------------------------------------------------------------

% \cvsect{Who Am I?}

% \begin{minipage}[t]{0.4\textwidth} % 40% of the page width for the introduction text
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
	
% 	\lorem \lorem \lorem \lorem \lorem\\ % Dummy text
% \end{minipage}
% \hfill % Whitespace between
% \begin{minipage}[t]{0.5\textwidth} % 50% of the page for the skills bar chart
% 	\vspace{-\baselineskip} % Required for vertically aligning minipages
% 	\begin{barchart}{5.5}
% 		\baritem{JavaScript}{60}
% 		\baritem{PHP}{100}
% 		\baritem{SASS/LESS}{70}
% 		\baritem{Bootstrap}{70}
% 		\baritem{Git}{40}
% 		\baritem{LaTeX}{60}
% 	\end{barchart}
% \end{minipage}

% \begin{center}
% 	\bubbles{5/Eclipse, 6/git, 4/Office, 3/Inkscape, 3/Blender}
% \end{center}

%----------------------------------------------------------------------------------------
%	SKILLS
%----------------------------------------------------------------------------------------

\cvsect{Technical Skills}

\textbf{Programming Languages} - JavaScript\slashsep
	TypeScript\slashsep
	C\#\\
	% Python\\
\textbf{Frameworks \& Libraries} - React\slashsep
	Next.js\slashsep
	Node.js\slashsep
	ASP.NET\slashsep
	SQL Server\\
\textbf{Tools \& Others} - Git\slashsep
 	Postman\slashsep
 	AWS\slashsep
 	Google Analytics\slashsep
 	GraphQL\\

%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------

\cvsect{Experience}

\begin{entrylist}
	\entry
		{2023 -- Present\\\footnotesize{Ecuador}}
		{Freelance Software Engineer}
		{}
		{
			\begin{itemize}
				\item Delivered end-to-end solutions for both local and international clients, combining technical implementation with strategic consulting to align software with business goals.
			\end{itemize}
		}
	\entry
		{2018 -- 2023\\\footnotesize{Baton Rouge, LA}}
		{React Engineer}
		{Acentra Health / Kepro / eQHealth Solutions}
		{
			\begin{itemize}
				\item Spearheaded React development efforts for a population health management and healthcare IT solutions suite, serving 70+ federal, state, and commercial clients in the USA.
				\item Executed the migration, optimization, and redesign of application views from ASP.NET Web Forms to React, enhancing user experience and decreasing load times by half.
				\item Resolved 500+ high-priority vulnerabilities and accessibility problems impacting the entire application suite, eliminating critical security incidents and improving integrity and usability.
				\item Implemented a React TypeScript admin dashboard for controlling system settings, permissions, and correspondence processing, eliminating manual tasks and halving turnaround time.
				\item Ensured that frontend components submitted by fellow engineers complied with requirements and current standards, reducing post-launch defects and securing positive client feedback.
			\end{itemize}
		}
	\entry
		{2015 -- 2018\\\footnotesize{New Orleans, LA}}
		{Software Developer}
		{CivicSource}
		{
			\begin{itemize}
				\item Overhauled tax management application by redesigning and migrating Razor views to React, streamlining admin work by improving usability and user experience.
				\item Enhanced tax and foreclosure sales application by developing 100+ new features (React JavaScript \& Redux, Knockout.js, C\#, SQL Server) and automated test cases (Mocha, MSTest).
				\item Led the design and development of a careers-centered website using Grunt, Metalsmith, and Handlebars, generating a 60\% upsurge in direct job applications.
				\item Conducted code reviews and performed candidate interviews in support of dev team expansion.
			\end{itemize}
		}
	\entry
		{2014 -- 2015\\\footnotesize{New Orleans, LA}}
		{Research Assistant}
		{University of New Orleans}
		{
			\begin{itemize}
				\item Engineered a forensic tool for API-based evidence acquisition from cloud storage services using Python and Flask, work published in \href{https://www.sciencedirect.com/science/article/abs/pii/S1742287616300536?via=ihub}{Elsevier's Digital Investigation Journal (Vol 18, Pages 79-95)}.
				\item Developed a lightweight infrastructure for hands-on network security education, integrating Docker, Vagrant, and AWS.
				\item Coached educators on core cybersecurity concepts in the NSA’s GenCyber program.
			\end{itemize}
		}
	\entry
		{2012 -- 2013\\\footnotesize{Guayaquil, Ecuador}}
		{Webmaster II}
		{Banco Territorial}
		{
			\begin{itemize}
				\item Directed 10+ high-priority enhancements and resolved multiple bugs for a transactional system.
				\item Established routine penetration tests on the transactional system and web applications, preemptively detecting and fixing of several security vulnerabilities.
				\item Programmed new microservices while collaborating with cross-functional teams, ensuring seamless integration of new features into other department operations.
			\end{itemize}
		}
	\entry
		{2011 -- 2012\\\footnotesize{Guayaquil, Ecuador}}
		{Webmaster}
		{Dinamo Consulting}
		{
			\begin{itemize}
				\item Built CMS-based web storefronts that drove digital transformation for the company clients.
			\end{itemize}
		}
\end{entrylist}

%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------

\cvsect{Education}

\begin{entrylist}
	\entry
		{2015\\\footnotesize{New Orleans, LA}}
		{Computer Science Master's Degree}
		{University of New Orleans}
		{
			Research assistant (2014 -- 2015)\slashsep
			Cybersecurity trainer (2014)
		}
	\entry
		{2011\\\footnotesize{Guayaquil, Ecuador}}
		{Computer Science Bachelor's Degree}
		{Escuela Superior Politécnica del Litoral - ESPOL}
		{
			Digital media production assistant (2010 -- 2011)
		}
\end{entrylist}

\end{document}
